Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-24 Methods-and-Results.tex
paragraph test
results structure added

\subsubsubsection{Intergroup Contact}

To test the prerequisite effect of intergroup contact, every `Experience
Recap' started with the question
``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''

@@

>>>>

\paragraph{Intergroup Contact}

To test the prerequisite effect of intergroup contact, every experience
sampling measurement started with the question
``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''
(31.59\% of all 1225 daily diary responses).

\paragraph{Psychological Needs}

\paragraph{Perceived Interaction Quality}

\paragraph{Outgroup Attitudes}

@@

\paragraph{Contact Hypothesis}

\paragraph{Core Need}

\begin{itemize}
\tightlist
\item
  Att \textasciitilde{} Need \& Qlt \textasciitilde{} Need
\item
  Att \textasciitilde{} Need + Qual
\end{itemize}

\paragraph{Robustness}
